Experience Report: Haskell in Computational Biology

### 2012-03-12 mrfy_experience_report.tex
delay marginal note about citing hood, hat, freya

@@

Like other functional programmers, we~have found that 
once we have our types right, our code is often right.
But~MRFy computes with arrays and array indices,
and in that domain, types don't help much.
Bounds violations lead to run-time errors, which we have not been able
to identify any systematic way to~debug.
GHC's profiler can provide stack traces, but we~found this information
difficult to discover, and as noted above,
there are barriers to profiling.
We're~aware that debugging lazy functional programs has been a topic
of some research,\remark{Do we cite Hood, Hat, or Freya?}
but one of the biggest barriers we encountered to using Haskell is
that we have had to abandon our old approaches to debugging,
and we~see no clear path to follow.

>>>>

\iffinaldraft
  \newcommand\finalremark{\remark}
\else
  \newcommand\finalremark[1]{\relax}
\fi

@@

Like other functional programmers, we~have found that 
once we have our types right, our code is often right.
But~MRFy computes with arrays and array indices,
and in that domain, types don't help much.
Bounds violations lead to run-time errors, which we have not been able
to identify any systematic way to~debug.
GHC's profiler can provide stack traces, but we~found this information
difficult to discover, and as noted above,
there are barriers to profiling.
We're~aware that debugging lazy functional programs has been a topic
of some research,\finalremark{Do we cite Hood, Hat, or Freya?}
but one of the biggest barriers we encountered to using Haskell is
that we have had to abandon our old approaches to debugging,
and we~see no clear path to follow.
